### 2013-12-28 thesis/src/chapters/chapter-5-design.tex
Thesis: removed redundant table

\subsection{Auto-scaling module}

@@

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralised and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

As \cite{IBM06} states, each autonomic component has modules that are responsible for:
\begin{itemize}
	\item monitoring
	\item analysis
	\item planning
	\item action execution
\end{itemize}

While the managed component has:
\begin{itemize}
	\item sensors
	\item effectors
\end{itemize}

\subsubsection{Monitoring}

@@

>>>>

\subsection{Auto-scaling subsystem}

@@

\subsubsection{Monitoring}
Monitoring module of each autonomic component aims to gather data from Sensors of a managed resource. While design of Cloud-SAP doesn't have any specific requirements regarding underlying monitoring mechanism there are a few aspects that should be taken into consideration. Table \ref{tab:monitoring-module-issues-summary} summarises main points.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ X X X }
\specialrule{.1em}{.05em}{.05em}
 & \textbf{Advantages} & \textbf{Disadvantages} \\ \specialrule{.1em}{.05em}{.05em}

\textbf{data exchange model} & & \\ \specialrule{.1em}{.05em}{.05em}
push based &
-- notification driven: all changes are reflected immediately in the system
&
-- requires additional agent at monitored component
\\ \hline
pull based & 
-- more calculations are being done at monitoring module side (doesn't involve additional load at managed component)
& 
-- some monitoring cycles can be redundant if scheduler is not properly tuned
\\ \hline

\textbf{data format} & & \\ \specialrule{.1em}{.05em}{.05em}
binary &
-- space-effective

-- unreadable for human
& \\ \hline
character-based &
-- human readable
&
-- ineffective in terms of space
\\ \hline

\textbf{communication protocol} & & \\ \specialrule{.1em}{.05em}{.05em}
vendor specific &
-- provides specific data to a given managed component (ie. virtual machine / container)
& 
-- may cause incompatibility problem while expanding cloud-sap system to a consecutive cloud instances
\\ \hline
standard-based &
-- supports scaling across multiple cloud instances as long as they support standard
&
-- gathered data may be inadequate to a specific needs
\\ \hline
\end{tabularx}

\caption{Monitoring - summary of issues}
\label{tab:monitoring-module-issues-summary}

\end{table}

Cloud-SAP is entirely focused on further data processing, consequently whether to store monitoring data or not is entirely implementation dependant.

Among the currently available monitoring systems remarkable are Cloud Watch \cite{CloudWatch}, OpenNebula (Information Manager / Virtual Machine Manager) \cite{OpenNebula} there are also open approaches such as Ganglia Monitoring System \cite{MaChCu04}.

@@

\subsubsection{Knowledge base}

\subsubsection{Hierarchical autonomic-system}
Due to the fact that designed platform operates on multiple layers, we can extend idea of an autonomic component by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralised and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

### 2013-12-28 thesis/src/chapters/chapter-7-evaluation.tex
Thesis: removed redundant table

\subsubsection{Hardware configuration}
All virtual machines were deployed on a host named \emph{Node1}, whose configuration can be found in table \ref{tbl:test-deployment-time-common-hardware-configuration}. Diagram presents the physical configuration of nodes.

+ fizycznych

>>>>

\subsubsection{Hardware configuration}

All virtual machines were deployed on a host named \emph{Node1}, whose configuration can be found in table \ref{tbl:test-deployment-time-common-hardware-configuration}. Diagram presents the physical configuration of nodes.
